### 2016-04-01 docs/ms_communitySynchrony.Rmd
SUBMITTED VERSION TO ELE

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{color}
- \usepackage{rotating}
layout: 12pt
linkcolor: black
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  word_document: default
urlcolor: black
---

@@

Figures
-------

```{r time_series_fig, echo=FALSE, include=TRUE, fig.width=8.5, fig.height=4, fig.cap="Observed time series of mean percent cover (averaged over quadrats for each year) and per capita growth rates for each species at each site. Panels are labeled by site codes: AZ = Arizona, ID = Idaho, KS = Kansas, MT = Montana, and NM = New Mexico.", eval=F}
out_ks$percent_cover$site <- "Kansas"
out_id$percent_cover$site <- "Idaho"
out_mt$percent_cover$site <- "Montana"
out_nm$percent_cover$site <- "New Mexico"
out_az$percent_cover$site <- "Arizona"
cover_data <- rbind(out_ks$percent_cover, out_id$percent_cover,
                    out_mt$percent_cover, out_nm$percent_cover, 
                    out_az$percent_cover)

>>>>

---
bibliography: ~/Dropbox/Bibliography/CommunitySynchrony.bib
csl: components/ecology.csl
fontsize: 12pt
geometry: margin=1in
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage{setspace}
- \usepackage{todonotes}
- \doublespacing
- \usepackage{color}
- \usepackage{rotating}
layout: 12pt
linkcolor: black
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    keep_tex: yes
urlcolor: black
---

@@

Figures
-------
```{r time_series_fig, echo=FALSE, include=TRUE, fig.width=8.5, fig.height=4, fig.cap="Observed time series of mean percent cover (averaged over quadrats for each year) and per capita growth rates for each species at each site. Panels are labeled by site codes: AZ = Arizona, ID = Idaho, KS = Kansas, MT = Montana, and NM = New Mexico.", eval=F}
out_ks$percent_cover$site <- "Kansas"
out_id$percent_cover$site <- "Idaho"
out_mt$percent_cover$site <- "Montana"
out_nm$percent_cover$site <- "New Mexico"
out_az$percent_cover$site <- "Arizona"
cover_data <- rbind(out_ks$percent_cover, out_id$percent_cover,
                    out_mt$percent_cover, out_nm$percent_cover, 
                    out_az$percent_cover)

### 2016-04-01 docs/ms_communitySynchrony.tex
SUBMITTED VERSION TO ELE

\textbf{Number of Words}: Abstract = 138; Main Text = 4929 (including section titles and in-line citations)

@@

\subsection{Tables}\label{tables}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/formatted_figure1.png}
  \caption{Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the upper and lower 95\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical predicion.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{./components/formatted_figures/formatted_figure3.png}
  \caption{Synchrony of species per capita growth rates simulated in large monocultures (IPM without species interactions) versus synchrony in large polycultures (IPM with species interactions). We used the same sequence of random year effects for both simulations (monoculture and polyculture) to mimic biodiversity-ecosystem functioning experiments. The dashed line is the line of equality. Simulation results in this figure are analagous to ``No Comp. + No D.S.'' (monocultures) and ``No D.S.'' (polycultures) in Fig. 1, but here we control the time series of random year effects.}
\end{figure}

@@

Vellend, M., L. Baeten, I. H. Myers-Smith, S. C. Elmendorf, R.
Beaus{é}jour, C. D. Brown, P. {De Frenne}, K. Verheyen, and S. Wipf.
2013. Global meta-analysis reveals no net change in local-scale plant
biodiversity over time. Proceedings of the National Academy of Sciences
of the United States of America 110:19456--9.

@@

>>>>

\textbf{Number of Words}: Abstract = 138; Main Text = 4965 (including section titles and in-line citations)

@@

@@

Vellend, M., L. Baeten, I. H. Myers-Smith, S. C. Elmendorf, R.
Beauséjour, C. D. Brown, P. {De Frenne}, K. Verheyen, and S. Wipf. 2013.
Global meta-analysis reveals no net change in local-scale plant
biodiversity over time. Proceedings of the National Academy of Sciences
of the United States of America 110:19456--9.

@@

\subsection{Table Titles}\label{tables}
TABLE 1: Site descriptions and focal species.

TABLE 2: Observed synchrony among species' per capita growth rates ($\phi_{R}$), observed synchrony among species' percent cover ($\phi_{C}$), the coefficient of variation of total community cover, and species richness for each community. Species richness values reflect the number of species analyzed from the community, not the actual richness.

\subsection{Tables}\label{tables}
\singlespacing

\subsection{Figures Captions}
\doublespacing

FIGURE 1: Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the upper and lower 95\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical prediction.

FIGURE 2: Synchrony of species' growth rates for each study area from IBM simulations across different landscape sizes when only demographic stochastcity is present (``D.S. Only'') and when environmental stochasticity is also present removed (``D.S. + E.S.''). The horizontal lines show the analytical predictions $\mathcal{M}_D$ (dashed line) and $\mathcal{M}_E$ (dotted line). The strength of demographic stochasticity decreases as landscape size increases because population sizes also increase. Theoretically, ``D.S. Only'' simulations should remain constant across landscape size, whereas ``D.S. + E.S.'' simulations should shift from the $\mathcal{M}_D$ prediction to the $\mathcal{M}_E$ prediction as landscape size, and thus population size, increases, but only if demographic stochasticity it strong enough to counteract environmental forcing. Error bars represent the upper and lower 95\% quantiles from model simulations.

FIGURE 3: Synchrony of species per capita growth rates simulated in large monocultures (IPM without species interactions) versus synchrony in large polycultures (IPM with species interactions). We used the same sequence of random year effects for both simulations (monoculture and polyculture) to mimic biodiversity-ecosystem functioning experiments. The dashed line is the line of equality. Simulation results in this figure are analogous to ``No Comp. + No D.S.'' (monocultures) and ``No D.S.'' (polycultures) in Fig. 1, but here we control the time series of random year effects.

\begin{figure}[!ht]
  \centering
      \includegraphics[width=6in]{./components/formatted_figures/formatted_figure1.png}
  \caption{Community-wide species synchrony of per capita growth rates from model simulation experiments. Synchrony of species' growth rates for each study area are from simulation experiments with demographic stochasticity, environmental stochasticity, and interspecific competition present (``All Drivers''), demographic stochasticity removed (``No D.S.''), environmental stochasticity removed (``No E.S.''), interspecific competition removed (``No Comp.''), interspecific competition and demographic stochasticity removed (``No Comp. + No D.S.''), and interspecific competition and environmental stochasticity removed (``No Comp. + No E.S.''). Abbreviations within the bars for the New Mexico site indicate whether the IBM or IPM was used for a particular simulation. Error bars represent the upper and lower 95\% quantiles from model simulations. All IBM simulations shown in this figure were run on a 25 $\text{m}^2$ virtual landscape. Points show observed and predicted synchrony aligned with the model simulation that corresponds with each observation or analytical prediction.}
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics[width=4in]{./components/formatted_figures/formatted_figure3.png}
  \caption{Synchrony of species per capita growth rates simulated in large monocultures (IPM without species interactions) versus synchrony in large polycultures (IPM with species interactions). We used the same sequence of random year effects for both simulations (monoculture and polyculture) to mimic biodiversity-ecosystem functioning experiments. The dashed line is the line of equality. Simulation results in this figure are analogous to ``No Comp. + No D.S.'' (monocultures) and ``No D.S.'' (polycultures) in Fig. 1, but here we control the time series of random year effects.}
\end{figure}

### 2016-04-01 docs/online_supporting_information.tex
SUBMITTED VERSION TO ELE

\begin{table}[ht]
\centering
\caption{Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\phi_{R,\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\phi_{R,\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\mathcal{M}_D$).} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & Predicted $\phi_{R,\mathcal{M}_D}$ & Simulated $\phi_{R,\mathcal{M}_D}$ & Predicted $\phi_{R,\mathcal{M}_E}$ & Simulated $\phi_{R,\mathcal{M}_E}$ \\ 
  \hline
New Mexico & 0.56 & 0.51 & 0.86 & 0.85 \\ 
  Arizona & 0.51 & 0.52 & 0.82 & 0.81 \\ 
  Kansas & 0.35 & 0.39 & 0.62 & 0.63 \\ 
  Montana & 0.31 & 0.33 & 0.47 & 0.49 \\ 
  Idaho & 0.29 & 0.31 & 0.43 & 0.41 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Percent differences of synchrony of per capita growth rates between each removal simulation experiment and the 'All Drivers' simulation.} 
\begin{tabular}{lrrrrr}
  \hline
simulation & 1New Mexico & 2Arizona & 3Kansas & 4Montana & 5Idaho \\ 
  \hline
1No D.S. & 5.00 & 4.94 & 7.13 & 4.42 & 10.10 \\ 
  2No Comp. + No D.S. & 4.25 & 2.08 & 7.61 & 4.39 & 8.10 \\ 
  4No Comp. & 0.98 & 0.06 & 4.84 & 1.01 & 0.11 \\ 
  5No E.S. & 40.14 & 33.20 & 47.84 & 38.52 & 9.28 \\ 
  6No Comp. + No E.S. & 45.95 & 41.48 & 38.21 & 33.07 & 20.33 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Comparisons between our analytical predictions and simulation results for synchrony of species' per capita growth rates. Analytical predictions represent two limiting cases where only demographic stochasticity is operating ($\phi_{R,\mathcal{M}_D}$) and where only environmental stochasticity is operating ($\phi_{R,\mathcal{M}_E}$). Simulated synchrony values come from our empirically-based, multi-species population models when simulated under conditions that match the limiting case conditions (e.g., environmental stochasticity and competition removed for $\mathcal{M}_D$).} 
{\normalsize
\begin{tabular}{lrrrr}
  \hline
Site & Predicted $\phi_{R,\mathcal{M}_D}$ & Simulated $\phi_{R,\mathcal{M}_D}$ & Predicted $\phi_{R,\mathcal{M}_E}$ & Simulated $\phi_{R,\mathcal{M}_E}$ \\ 
  \hline
New Mexico & 0.56 & 0.51 & 0.86 & 0.86 \\ 
  Arizona & 0.51 & 0.52 & 0.82 & 0.82 \\ 
  Kansas & 0.35 & 0.39 & 0.62 & 0.62 \\ 
  Montana & 0.31 & 0.33 & 0.47 & 0.49 \\ 
  Idaho & 0.29 & 0.31 & 0.43 & 0.41 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Percent differences of synchrony of per capita growth rates between each removal simulation experiment and the 'All Drivers' simulation.} 
\begin{tabular}{lrrrrr}
  \hline
simulation & 1New Mexico & 2Arizona & 3Kansas & 4Montana & 5Idaho \\ 
  \hline
1No D.S. & 4.82 & 3.99 & 7.19 & 5.37 & 9.53 \\ 
  2No Comp. + No D.S. & 4.74 & 2.70 & 6.81 & 4.53 & 7.69 \\ 
  4No Comp. & 0.98 & 0.06 & 4.84 & 1.01 & 0.11 \\ 
  5No E.S. & 40.14 & 33.20 & 47.84 & 38.52 & 9.28 \\ 
  6No Comp. + No E.S. & 45.95 & 41.48 & 38.21 & 33.07 & 20.33 \\ 
   \hline
\end{tabular}
\end{table}
